<!-- R Commander Markdown Template -->

Replace with Main Title
=======================

### user

### `r as.character(Sys.Date())`

```{r echo=FALSE}
# include this code chunk as-is to set options
knitr::opts_chunk$set(comment=NA, prompt=TRUE, out.width=750, fig.height=8, fig.width=8)
library(Rcmdr)
library(car)
library(RcmdrMisc)
```

```{r}


### Scatterplot Matrix: ~Cooling_Load+Glazing_Area_Distribution+Relative_Compactness+Surface_Area
```{r}
scatterplotMatrix(~Cooling_Load+Glazing_Area_Distribution+Relative_Compactness+Surface_Area,
   regLine=FALSE, smooth=FALSE, diagonal=list(method="density"), data=EED)
```


### Histogram: Cooling_Load
```{r}
with(EED, Hist(Cooling_Load, groups=Orientation, scale="frequency", 
  breaks="Sturges", col="darkgray"))
```


### Discrete Distribution Plot: Glazing_Area
```{r}
with(EED, discretePlot(Glazing_Area, scale="frequency"))
```


### Discrete Distribution Plot: Overall_Height
```{r}
with(EED, discretePlot(Overall_Height, scale="frequency"))
```

{
### Discrete Distribution Plot: Glazing_Area
} {
### Discrete Distribution Plot: Overall_Height
} {
### Discrete Distribution Plot: Relative_Compactness
} {
### Discrete Distribution Plot: Roof_Area
}```{r}
with(EED, discretePlot(Glazing_Area, scale="frequency"))
with(EED, discretePlot(Overall_Height, scale="frequency"))
with(EED, discretePlot(Relative_Compactness, scale="frequency"))
with(EED, discretePlot(Roof_Area, scale="frequency"))
```


### Scatterplot Matrix: ~Cooling_Load+Glazing_Area+Glazing_Area_Distribution+Heating_Load+Overall_Height+Relative_Compactness
```{r}
scatterplotMatrix(~Cooling_Load+Glazing_Area+Glazing_Area_Distribution+Heating_Load+Overall_Height+Relative_Compactness,
   regLine=FALSE, smooth=FALSE, diagonal=list(method="density"), data=EED)
```

